---
title: "Probability"
output:
  pdf_document: default
  html_document:
    code_folding: hide
    css: ./lab.css
    highlight: pygments
    theme: cerulean
---

```{r load-data, eval=TRUE,include=FALSE}
load("more/kobe.RData")
head(kobe)
```



```{r first9, eval=TRUE,include=FALSE}
kobe$basket[1:9]
```

1.  What does a streak length of 1 mean, i.e. how many hits and misses are in a 
    streak of 1? What about a streak length of 0?  
    <b>A streak of length 1 indicates a hit followed by a miss. A streak of length 0 indicates a miss followed by a miss.</b>

```{r calc-streak-kobe, eval=TRUE,include=FALSE}
kobe_streak <- calc_streak(kobe$basket)
barplot(table(kobe_streak))
```

2.  Describe the distribution of Kobe's streak lengths from the 2009 NBA finals. 
    What was his typical streak length? How long was his longest streak of baskets?  
    <b>His most frequent (and therefore "typical") <b>streak</b> length is 1; his longest streak of baskets was 4.</b>
```{r message=FALSE,warning=FALSE}
median(kobe_streak)
table(kobe_streak)
```


```{r head-tail, eval=TRUE}
outcomes <- c("heads", "tails")
sample(outcomes, size = 1, replace = TRUE)
```


```{r sim-fair-coin, eval=TRUE}
sim_fair_coin <- sample(outcomes, size = 100, replace = TRUE)
```



```{r table-sim-fair-coin, eval=TRUE}
sim_fair_coin
table(sim_fair_coin)
```



```{r sim-unfair-coin, eval=TRUE}
sim_unfair_coin <- sample(outcomes, size = 100, replace = TRUE, prob = c(0.2, 0.8))
```

`prob=c(0.2, 0.8)` indicates that for the two elements in the `outcomes` vector,
we want to select the first one, `heads`, with probability 0.2 and the second 
one, `tails` with probability 0.8. Another way of thinking about this is to 
think of the outcome space as a bag of 10 chips, where 2 chips are labeled 
"head" and 8 chips "tail". Therefore at each draw, the probability of drawing a 
chip that says "head"" is 20%, and "tail" is 80%.

3.  In your simulation of flipping the unfair coin 100 times, how many flips 
    came up heads?  
    <b><em>Please see table below.</em> Heads came up `r table(sim_unfair_coin)[1]` times.</b>
```{r message=FALSE,warning=FALSE}
table(sim_unfair_coin)

```    


```{r sim-basket, eval=TRUE}
outcomes <- c("H", "M")
sim_basket <- sample(outcomes, size = 1, replace = TRUE)
```


4.  What change needs to be made to the `sample` function so that it reflects a 
    shooting percentage of 45%? Make this adjustment, then run a simulation to 
    sample 133 shots. Assign the output of this simulation to a new object called
    `sim_basket`.  
    <b><em>See code below.</em><b>
```{r sim-basket2, eval=TRUE}
outcomes <- c("H", "M")
sim_basket <- sample(outcomes, size = 133, replace = TRUE, prob = c(0.45, 0.55))
table(sim_basket)
```

### Comparing Kobe Bryant to the Independent Shooter

Using `calc_streak`, compute the streak lengths of `sim_basket`.
```{r message=FALSE,warning=FALSE}
sim_player<-calc_streak(sim_basket)
sim_player
```

5.  </b></strong><span style="font-weight:normal;">Describe the distribution of streak lengths. What is the typical streak 
    length for this simulated independent shooter with a 45% shooting percentage?
    How long is the player's longest streak of baskets in 133 shots?</span>  
    <b>The most frequent (and therefore "typical") <em>streak</em> length is 1; the longest streak of baskets is 6.</b>
```{r warning=FALSE,message=FALSE}
median(sim_player)
table(sim_player)
barplot(table(sim_player))
```

6.  </b>If you were to run the simulation of the independent shooter a second time, 
    how would you expect its streak distribution to compare to the distribution 
    from the question above? Exactly the same? Somewhat similar? Totally 
    different? Explain your reasoning.  
    <b>I would expect the distribution to be different. While we have set the probability of hits and misses (probability of a shot being made set at 0.45), the distribution of streaks will be random.</b>

7.  </b>How does Kobe Bryant's distribution of streak lengths compare to the 
    distribution of streak lengths for the simulated shooter? Using this 
    comparison, do you have evidence that the hot hand model fits Kobe's 
    shooting patterns? Explain.  
    <b>The distribution of streaks are similar; the simulated player streak range was wider, including 3 streaks with length greater than Kobe's maximum length. While both the sim player and Kobe had similar numbers of consecutive misses (40 and 39 respectively), Kobe approximately doubled the sim player's streak frequency of length 1. Streak lengths of 2 and 3 were similarly distributed for the simulated player and Kobe. Though both players had approximately the same amount amounts of hits and misses, the simulated player was more likely to make baskets in longer streaks.</b> 

